---
title: "Society-aligned output analyses"
output:
  word_document:
    toc: yes
    keep_md: yes  
  html_notebook:
    code_folding: hide
    toc: yes  
---

```{r setup}
knitr::opts_chunk$set(cache = TRUE, cache.path = here::here("cache/"), cache.change_to_flush = 0, message = FALSE, warning = FALSE, dpi = 300, fig.retina = 2, fig.width = 8)
source(here::here("src/common_basis.R"))
```

```{r gdrive_version, eval=FALSE}
library(googledrive)
rmarkdown::render(here("src/jiemakel/society_related_output_analysis.Rmd"),rmarkdown::word_document(toc=TRUE,keep_md=TRUE))
drive_put(here("src/jiemakel/society_related_output_analysis.docx"), path = as_id("161toNA4jUgTzMjndSDVp1kpL9yGfHkwG"), name = "society_related_output_analysis", type = "application/vnd.google-apps.document")
```


# Society-aligned output by member through time

In the following, we 

1. first calculate for each member the number of society-related printings they have a substantive relationship to, 
1. limit only to members for whom we have a time of admission (earliest estimate), and
1. plot each such member on the graph with x=time of their admission and y=number of society-related printings contributed to.
1. Further, we calculate a loess-smoothed average for the number of printings contributed to per member through time.

## Overall

```{r}
periods <- tribble(~period,~start_year,~end_year,
                   "Köthen", 1617L, 1650L,
                   "Weimar", 1651L, 1662L,
                   "Halle", 1667L, 1680L
)

p <- p_to_a %>%
  inner_join(fbs_purpose_related_p) %>%
  inner_join(a_id_to_fbs_member_number) %>%
  filter(
    field_code %in% c("028A", "028B", "028C"),
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
      "^Adressat",
      "Erwähnte",
      "Gefeierte",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "Respondent",
      "Sonstige Person, Familie und Körperschaft",
      "Verfasser",
      "Vertragspartner",
      "Widmende",
      "Widmungsempfänger",
      "Drucker",
      "Zensor",
      "Beiträger",
      "GeistigeR Schöpfer",
      "Mitwirkender",
      "Herausgeber",
      "Angeklagte",
      "Auftraggeber"
    ), collapse = "|^"))
  ) %>%
  inner_join(fbs_metadata) %>%
  filter(field_code %in% c("028A", "028B") | is.na(rank_and_position) | !str_detect(rank_and_position,"graf|herzog|fürst")) %>%
  group_by(member_number) %>%
  summarise(works=n_distinct(p_id)) %>%
  right_join(fbs_metadata) %>%
  collect() %>%
  complete(nesting(member_number,earliest_year_of_admission),fill=list(works=0)) %>%
  inner_join(periods,join_by(earliest_year_of_admission>=start_year,earliest_year_of_admission<=end_year)) %>%
  mutate(label=str_c(member_number,": ",family_name,", ", first_name)) %>%
  ggplot(aes(x=earliest_year_of_admission,y=works)) +
  scale_x_continuous(breaks=seq(1600,1700,by=10)) +
  ylab("Mean contributions per member joining (N)") +
  xlab("Year of admission") +
  geom_smooth(span=0.3) +
  geom_point(data=. %>% group_by(period, earliest_year_of_admission) %>% summarise(works=mean(works))) +
  scale_y_continuous(breaks=seq(0,20,by=2)) +
  theme_hsci_discrete() +
  theme(legend.position = "bottom") +
  coord_cartesian(ylim=c(0,NA))

save_plots(here("src/jiemakel/figures"),"mean_printings_per_member", p, width=8, height=6)
```
```{r}
periods <- tribble(~start_year,~end_year,~period,
1617L,1623L, "Köthen",
1624L,1630L, "Köthen",
1631L,1637L, "Köthen",
1638L,1644L, "Köthen",
1644L,1650L, "Köthen",
1651L,1656L, "Weimar",
1657L,1662L, "Weimar",
1667L,1673L, "Halle",
1674L,1680L, "Halle"
) %>% mutate(period_range=factor(str_c(start_year,"-",end_year)))

d <- p_to_a %>%
  inner_join(fbs_purpose_related_p) %>%
  inner_join(a_id_to_fbs_member_number) %>%
  filter(
    field_code %in% c("028A", "028B", "028C"),
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
      "^Adressat",
      "Erwähnte",
      "Gefeierte",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "Respondent",
      "Sonstige Person, Familie und Körperschaft",
      "Verfasser",
      "Vertragspartner",
      "Widmende",
      "Widmungsempfänger",
      "Drucker",
      "Zensor",
      "Beiträger",
      "GeistigeR Schöpfer",
      "Mitwirkender",
      "Herausgeber",
      "Angeklagte",
      "Auftraggeber"
    ), collapse = "|^"))
  ) %>%
  inner_join(fbs_metadata) %>%
  filter(field_code %in% c("028A", "028B") | is.na(rank_and_position) | !str_detect(rank_and_position,"graf|herzog|fürst")) %>%
  group_by(member_number) %>%
  summarise(works=n_distinct(p_id)) %>%
  right_join(fbs_metadata) %>%
  collect() %>%
  complete(nesting(member_number,earliest_year_of_admission),fill=list(works=0)) %>%
  inner_join(periods,join_by(earliest_year_of_admission>=start_year,earliest_year_of_admission<=end_year)) %>%
  mutate(period_range=fct_rev(period_range),printings=fct_relevel(case_when(
    works==0 ~ "0",
    works==1 ~ "1",
    works>=2 & works<5 ~ "2-4",
    works>=5 & works<10 ~ "5-9",
    works>=10 & works<20 ~ "10-19",
    works>=20 ~ ">=20"
  ), "0","1","2-4","5-9","10-19",">=20")) %>%
  mutate(label=str_c(member_number,": ",family_name,", ", first_name)) %>%
  count(period_range,printings) %>%
  group_by(period_range) %>%
  mutate(prop=n/sum(n)) %>%
  ungroup()
```


```{r}
p <- d %>%
  group_by(period_range) %>%
  mutate(tn=sum(n)) %>%
  ungroup() %>%
  mutate(period_range=fct(str_c(period_range," (N=",tn,")"))) %>%
  filter(printings!="0") %>%
  ggplot(aes(x=period_range,y=prop,group=printings,fill=printings)) +
  ylab("Proportion of members") +
  xlab("Period of admission") +
  geom_col(position='stack') +
  theme_hsci_discrete() +
  theme(legend.position = "bottom") +
  scale_y_continuous(labels=scales::percent) +
  scale_coloropt(limits=c(">=20","10-19","5-9", "2-4", "1")) +
  labs(fill="Printings associated with member (N)") +
  coord_flip()

save_plots(here("src/jiemakel/figures"),"member_printing_groups", p, width=8, height=4)
```


```{r}
d %>%
  group_by(period_range) %>%
  mutate(tn=sum(n)) %>%
  ungroup() %>%
  mutate(period_range=fct(str_c(period_range," N=(",tn,")"))) %>%
  ggplot(aes(x=period_range,y=n,group=printings,fill=printings)) +
  ylab("Proportion of members") +
  xlab("Period of admission") +
  geom_col(position='stack') +
  theme_hsci_discrete() +
  theme(legend.position = "bottom") +
  scale_coloropt(limits=c(">=20","10-19","5-9", "2-4", "1", "0")) +
  labs(fill="Printings associated with member (N)") +
  coord_flip()
```

```{r}
df
```


```{r}
p1 <- p_to_a %>%
  inner_join(fbs_purpose_related_p) %>%
  inner_join(a_id_to_fbs_member_number) %>%
  filter(
    field_code %in% c("028A", "028B", "028C"),
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
      "^Adressat",
      "Erwähnte",
      "Gefeierte",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "Respondent",
      "Sonstige Person, Familie und Körperschaft",
      "Verfasser",
      "Vertragspartner",
      "Widmende",
      "Widmungsempfänger",
      "Drucker",
      "Zensor",
      "Beiträger",
      "GeistigeR Schöpfer",
      "Mitwirkender",
      "Herausgeber",
      "Angeklagte",
      "Auftraggeber"
    ), collapse = "|^"))
  ) %>% 
  group_by(member_number) %>%
  summarise(works=n_distinct(p_id)) %>%
  mutate(dataset="base set") %>%
  union_all(
    p_to_a %>%
    inner_join(fbs_purpose_related_p) %>%
    inner_join(a_id_to_fbs_member_number) %>%
    filter(
      field_code %in% c("028A", "028B", "028C"),
      is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
      is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
        "^Adressat",
        "Erwähnte",
        "Gefeierte",
        "Mitglied eines Ausschusses, der akademische Grade vergibt",
        "Normerlassende Gebietskörperschaft",
        "Praeses",
        "Respondent",
        "Sonstige Person, Familie und Körperschaft",
        "Verfasser",
        "Vertragspartner",
        "Widmende",
        "Widmungsempfänger",
        "Drucker",
        "Zensor",
        "Beiträger",
        "GeistigeR Schöpfer",
        "Mitwirkender",
        "Herausgeber",
        "Angeklagte",
        "Auftraggeber"
      ), collapse = "|^"))
    ) %>%
    inner_join(fbs_metadata) %>%
    filter(field_code %in% c("028A", "028B") | is.na(rank_and_position) | !str_detect(rank_and_position,"graf|herzog|fürst")) %>%
    group_by(member_number) %>%
    summarise(works=n_distinct(p_id)) %>%
    mutate(dataset="028C graf, herzog, fürst removed")
  ) %>%
  right_join(fbs_metadata) %>%
  collect() %>%
  complete(dataset,nesting(member_number,earliest_year_of_admission),fill=list(works=0)) %>%
  filter(!is.na(dataset)) %>%
  mutate(label=str_c(member_number,": ",family_name,", ", first_name)) %>%
  ggplot(aes(x=earliest_year_of_admission,y=works,color=dataset,fill=dataset)) +
  scale_x_continuous(breaks=seq(1600,1700,by=10)) +
  ylab("Society-related printings substantively contributed to (N)") +
  xlab("Year of admission") +
  theme_hsci_discrete()
 
p1 + 
  geom_smooth(span=0.3) +
  geom_point(data=. %>% group_by(earliest_year_of_admission,dataset) %>% summarise(works=mean(works))) +
  scale_y_continuous(breaks=seq(0,10,by=1)) +
  theme(legend.position = "bottom") +
  coord_cartesian(ylim=c(0,NA))

(p1 + 
  scale_y_continuous(breaks=seq(0,500,by=50)) +
  geom_jitter(aes(text=label),size=0.5, height=0) +
  geom_smooth(span=0.3)
) %>%
  ggplotly(width=1024,height=768)
```

```{r}
periods <- tribble(~period,~start_year,~end_year,
                   "Köthen", 1617L, 1650L,
                   "Weimar", 1651L, 1667L,
                   "Halle", 1668L, 1680L
)
d <- p_to_a %>%
  inner_join(fbs_purpose_related_p) %>%
  inner_join(a_id_to_fbs_member_number) %>%
  filter(
    field_code %in% c("028A", "028B", "028C"),
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
      "^Adressat",
      "Erwähnte",
      "Gefeierte",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "Respondent",
      "Sonstige Person, Familie und Körperschaft",
      "Verfasser",
      "Vertragspartner",
      "Widmende",
      "Widmungsempfänger",
      "Drucker",
      "Zensor",
      "Beiträger",
      "GeistigeR Schöpfer",
      "Mitwirkender",
      "Herausgeber",
      "Angeklagte",
      "Auftraggeber"
    ), collapse = "|^"))
  ) %>% 
  group_by(member_number) %>%
  summarise(works=n_distinct(p_id)) %>%
  mutate(dataset="base set") %>%
  union_all(
    p_to_a %>%
    inner_join(fbs_purpose_related_p) %>%
    inner_join(a_id_to_fbs_member_number) %>%
    filter(
      field_code %in% c("028A", "028B", "028C"),
      is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
      is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
        "^Adressat",
        "Erwähnte",
        "Gefeierte",
        "Mitglied eines Ausschusses, der akademische Grade vergibt",
        "Normerlassende Gebietskörperschaft",
        "Praeses",
        "Respondent",
        "Sonstige Person, Familie und Körperschaft",
        "Verfasser",
        "Vertragspartner",
        "Widmende",
        "Widmungsempfänger",
        "Drucker",
        "Zensor",
        "Beiträger",
        "GeistigeR Schöpfer",
        "Mitwirkender",
        "Herausgeber",
        "Angeklagte",
        "Auftraggeber"
      ), collapse = "|^"))
    ) %>%
    inner_join(fbs_metadata) %>%
    filter(field_code %in% c("028A", "028B") | is.na(rank_and_position) | !str_detect(rank_and_position,"graf|herzog|fürst")) %>%
    group_by(member_number) %>%
    summarise(works=n_distinct(p_id)) %>%
    mutate(dataset="028C graf, herzog, fürst removed")
  ) %>%
  right_join(fbs_metadata) %>%
  collect() %>%
  complete(dataset,nesting(member_number,earliest_year_of_admission),fill=list(works=0)) %>%
  filter(!is.na(dataset))

d %>% 
  inner_join(periods, join_by(earliest_year_of_admission>=start_year,earliest_year_of_admission<=end_year)) %>%
  group_by(period, dataset) %>%
  summarise(mean_printings=mean(works)) %>%
  relocate(dataset,period,mean_printings) %>%
  arrange(dataset,period)
```

```{r}
periods <- tribble(~start_year,~end_year,~period,
1617L,1623L, "Köthen",
1624L,1630L, "Köthen",
1631L,1637L, "Köthen",
1638L,1644L, "Köthen",
1644L,1650L, "Köthen",
1651L,1656L, "Weimar",
1657L,1662L, "Weimar",
1667L,1673L, "Halle",
1674L,1680L, "Halle"
) %>% mutate(period_range=factor(str_c(start_year,"-",end_year)))

p_to_a %>%
  inner_join(fbs_purpose_related_p) %>%
  inner_join(a_id_to_fbs_member_number) %>%
  filter(
    field_code %in% c("028A", "028B", "028C"),
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
      "^Adressat",
      "Erwähnte",
      "Gefeierte",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "Respondent",
      "Sonstige Person, Familie und Körperschaft",
      "Verfasser",
      "Vertragspartner",
      "Widmende",
      "Widmungsempfänger",
      "Drucker",
      "Zensor",
      "Beiträger",
      "GeistigeR Schöpfer",
      "Mitwirkender",
      "Herausgeber",
      "Angeklagte",
      "Auftraggeber"
    ), collapse = "|^"))
  ) %>% 
  inner_join(fbs_metadata) %>%
  filter(field_code %in% c("028A", "028B") | is.na(rank_and_position) | !str_detect(rank_and_position,"graf|herzog|fürst")) %>%
  group_by(member_number) %>%
  summarise(works=n_distinct(p_id)) %>%
  right_join(fbs_metadata) %>%
  replace_na(list(works=0)) %>%
  collect() %>%
  inner_join(periods, join_by(earliest_year_of_admission>=start_year,earliest_year_of_admission<=end_year)) %>%
  group_by(period_range) %>%
  summarise(published_min_one=sum(works>=1)/n(),published_min_two=sum(works>=2)/n(),published_min_five=sum(works>=5)/n(),published_min_ten=sum(works>=10)/n(),published_min_twenty=sum(works>=20)/n(), published_min_fifty=sum(works>=50)/n()) %>%
  gt() %>%
  fmt_percent() %>%
  fmt_passthrough(period_range)

```


## By genre

```{r}
p <- p_to_a %>%
  inner_join(fbs_purpose_related_p) %>%
  inner_join(a_id_to_fbs_member_number) %>%
  filter(
    field_code %in% c("028A", "028B", "028C"),
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
      "^Adressat",
      "Erwähnte",
      "Gefeierte",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "Respondent",
      "Sonstige Person, Familie und Körperschaft",
      "Verfasser",
      "Vertragspartner",
      "Widmende",
      "Widmungsempfänger",
      "Drucker",
      "Zensor",
      "Beiträger",
      "GeistigeR Schöpfer",
      "Mitwirkender",
      "Herausgeber",
      "Angeklagte",
      "Auftraggeber"
    ), collapse = "|^"))
  ) %>% 
  left_join(p_genre) %>%
  left_join(genre_categorisation) %>%
  filter(is.na(full_genre) | group_1=="Society-related") %>%
  inner_join(fbs_metadata) %>%
  filter(field_code %in% c("028A", "028B") | is.na(rank_and_position) | !str_detect(rank_and_position,"graf|herzog|fürst")) %>%
  group_by(member_number, group_3) %>%
  summarise(works=n_distinct(p_id), .groups="drop") %>%
  right_join(fbs_metadata) %>%
  mutate(label=str_c(member_number,": ",family_name,", ", first_name)) %>%
  collect() %>%
  complete(earliest_year_of_admission, group_3, fill=list(works=0)) %>%
  ggplot(aes(x=earliest_year_of_admission,y=works)) + 
  geom_jitter(aes(text=label),size=0.5, height=0) +
  geom_smooth(span=0.3) +
  scale_x_continuous(breaks=seq(1600,1700,by=20)) +
  ylab("Society-related printings substantively contributed to (N)") +
  xlab("Year of admission") +
  facet_wrap(~group_3, scales="free_y") +
  theme_hsci_discrete()

save_plots(here("src/jiemakel/figures"),"mean_printings_by_genre", p, width=8, height=6)
```


```{r}
(p_to_a %>%
  inner_join(fbs_purpose_related_p) %>%
  inner_join(a_id_to_fbs_member_number) %>%
  filter(
    field_code %in% c("028A", "028B", "028C"),
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
      "^Adressat",
      "Erwähnte",
      "Gefeierte",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "Respondent",
      "Sonstige Person, Familie und Körperschaft",
      "Verfasser",
      "Vertragspartner",
      "Widmende",
      "Widmungsempfänger",
      "Drucker",
      "Zensor",
      "Beiträger",
      "GeistigeR Schöpfer",
      "Mitwirkender",
      "Herausgeber",
      "Angeklagte",
      "Auftraggeber"
    ), collapse = "|^"))
  ) %>% 
  left_join(p_genre) %>%
  left_join(genre_categorisation) %>%
  filter(is.na(full_genre) | group_1=="Society-related") %>%
  inner_join(fbs_metadata) %>%
  filter(field_code %in% c("028A", "028B") | is.na(rank_and_position) | !str_detect(rank_and_position,"graf|herzog|fürst")) %>%
  group_by(member_number, group_3) %>%
  summarise(works=n_distinct(p_id), .groups="drop") %>%
  right_join(fbs_metadata) %>%
  mutate(label=str_c(member_number,": ",family_name,", ", first_name)) %>%
  collect() %>%
  complete(earliest_year_of_admission, group_3, fill=list(works=0)) %>%
  ggplot(aes(x=earliest_year_of_admission,y=works)) + 
  geom_jitter(aes(text=label),size=0.5, height=0) +
  geom_smooth(span=0.3) +
  scale_x_continuous(breaks=seq(1600,1700,by=10)) +
  ylab("Society-related printings substantively contributed to (N)") +
  xlab("Year of admission") +
  facet_wrap(~group_3, scales="free_y") +
  theme_hsci_discrete()) %>%
  ggplotly(width=1024,height=768)
```

# Proportion of admitted members with substantive contributions to society-related printings

```{r}
periods <- tribble(~start_year,~end_year,~period,
1617L,1623L, "Köthen",
1624L,1630L, "Köthen",
1631L,1637L, "Köthen",
1638L,1644L, "Köthen",
1645L,1650L, "Köthen",
1651L,1656L, "Weimar",
1657L,1662L, "Weimar",
1667L,1673L, "Halle",
1674L,1680L, "Halle"
) %>% mutate(period_range=factor(str_c(start_year,"-",end_year)))

p_to_a %>%
  inner_join(fbs_purpose_related_p) %>%
  inner_join(a_id_to_fbs_member_number) %>%
  filter(
    field_code %in% c("028A", "028B", "028C"),
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c( # role2 should not be one of these
      "^Adressat",
      "Erwähnte",
      "Gefeierte",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "Respondent",
      "Sonstige Person, Familie und Körperschaft",
      "Verfasser",
      "Vertragspartner",
      "Widmende",
      "Widmungsempfänger",
      "Drucker",
      "Zensor",
      "Beiträger",
      "GeistigeR Schöpfer",
      "Mitwirkender",
      "Herausgeber",
      "Angeklagte",
      "Auftraggeber"
    ), collapse = "|^"))
  ) %>% 
  inner_join(fbs_metadata) %>%
  filter(field_code %in% c("028A", "028B") | is.na(rank_and_position) | !str_detect(rank_and_position,"graf|herzog|fürst")) %>%
  group_by(member_number) %>%
  summarise(works=n_distinct(p_id)) %>%
  right_join(fbs_metadata) %>%
  replace_na(list(works=0)) %>%
  mutate(publishing=works>0) %>%
  collect() %>%
  inner_join(periods, join_by(earliest_year_of_admission>=start_year,earliest_year_of_admission<=end_year)) %>%
  group_by(period_range,period) %>%
  summarise(members_joined=n(),prop_publishing=sum(publishing)/n()) %>%
  ggplot(aes(x=period_range,y=prop_publishing, fill=period)) + 
  geom_col() +
  geom_text(aes(label=members_joined), nudge_y=-0.02, color="white") +
  scale_x_discrete() +
  scale_y_continuous(labels=scales::percent) +
  ylab("Proportion in publishing") +
  xlab("Period of admission") +
  theme_hsci_discrete() +
  theme(legend.position="bottom")
```

Numbers denote the number of members joining in each period.

# Society-purpose -related publications by genre through time

## Absolute

```{r}
p_year %>%
  filter(year>=1600,year<1700) %>%
  inner_join(fbs_purpose_related_p) %>%
  left_join(p_genre) %>%
  left_join(genre_categorisation) %>%
  filter(is.na(full_genre) | group_1=="Society-related") %>%
  mutate(decade=floor(year/10)*10) %>%
  count(group_3,decade) %>%
  collect() %>%
  complete(group_3, decade, fill=list(n=0)) %>%
  ggplot(aes(x=decade,y=n)) +
  geom_smooth(span=0.3) +
  geom_point() +
  coord_cartesian(ylim=c(0,NA)) +
  scale_x_continuous(breaks=seq(1600,1700,by=20)) +
  ylab("Printings by members (N)") +
  xlab("Decade") +
  facet_wrap(~group_3, scales="free_y") +
  theme_hsci_discrete()
```

## Normalised by number of members

```{r}
members_by_year <- tibble(year=1617:1699) %>% 
  inner_join(fbs_metadata %>% collect(), join_by(year>=earliest_year_of_admission,year<=latest_year_of_death)) %>%
  count(year) %>%
  right_join(tibble(year=1617:1699)) %>%
  replace_na(list(n=0))
```

```{r}
p_year %>%
  filter(year>=1600,year<1700) %>%
  inner_join(fbs_purpose_related_p) %>%
  left_join(p_genre) %>%
  left_join(genre_categorisation) %>%
  filter(is.na(full_genre) | group_1=="Society-related") %>%
  mutate(decade=floor(year/10)*10) %>%
  count(group_3,decade) %>%
  collect() %>%
  complete(group_3, decade, fill=list(n=0)) %>%
  inner_join(members_by_year %>% 
               mutate(decade=floor(year/10)*10) %>%
               group_by(decade) %>%
               summarise(mean_members=mean(n),.groups="drop")) %>%
  ggplot(aes(x=decade,y=n/mean_members)) +
  geom_smooth(span=0.3) +
  geom_point() +
  coord_cartesian(ylim=c(0,NA)) +
  scale_x_continuous(breaks=seq(1600,1700,by=20)) +
  ylab("Printings per member") +
  xlab("Decade") +
  facet_wrap(~group_3, scales="free_y") +
  theme_hsci_discrete()
```

## Proportion of publications by genre

```{r}
t <- p_year %>%
  filter(year>=1600,year<1700) %>%
  inner_join(fbs_purpose_related_p) %>%
  left_join(p_genre) %>%
  left_join(genre_categorisation) %>%
  filter(is.na(full_genre) | group_1=="Society-related") %>%
  mutate(decade=floor(year/10)*10)

t %>%
  group_by(decade) %>%
  summarise(total_n=n_distinct(p_id)) %>%
  inner_join(t %>%
    count(group_3, decade)
  ) %>%
  mutate(prop=n/total_n) %>%
  collect() %>%
  complete(group_3, decade, fill=list(prop=0)) %>%
  ggplot(aes(x=decade,y=prop)) +
  geom_smooth(span=0.3) +
  geom_point() +
  coord_cartesian(ylim=c(0,NA)) +
  scale_x_continuous(breaks=seq(1600,1700,by=20)) +
  scale_y_continuous(labels=scales::percent) +
  ylab("Society printings by genre (%)") +
  xlab("Decade") +
  facet_wrap(~group_3, scales="free_y") +
  theme_hsci_discrete()
```


